### 2023-09-03 sections/2-methods.tex
results

\subsection {Index-Building and Sharded Search}
\label{subsec:methods:index-building}
In this work, we also introduce the method of \emph{sharding} for $k$-nearest neighbors search.
With this approach, we aim to leverage the fact that $\rho$-nearest neighbors search is typically 
much faster than $k$-nearest neighbors search.

We begin by randomly partitioning the dataset into $s$ shards, where $s$ is determined based 
on some naive auto-tuning. On the first shard, we perform 
$k$-nearest neighbors search using one of the four algorithms described in Section~\ref{subsec:methods:knn-search}.
The result of this search will give us the $k$ closest neighbors to the query \emph{in the first shard}. We take the furthest of 
those $k$ neighbors and use its distance from the query as the radius to be used with $\rho$-nearest neighbors search (see Section~\ref{subsec:methods:rnn-search}) 
on each remaining shard. We then take the union of the results of these $\rho$-nearest neighbors searches, along with the $k$ neighbors
from the first shard, and then linear search over those points to find the actual $k$ nearest neighbors.

Note that the size of the shards is not necessarily consistent; it is often optimal to have the first shard be smaller than the others,
since the first shard is the only one for which we perform $k$-nearest neighbors search. However, making this first shard too small
introduces the risk of significantly overestimating the radius (i.e., the distance to the $k$-th ), resulting in much slower $\rho$-nearest neighbors search on the subsequent shards.
Finding the precise optimal ratio between the size of the first shard and the size of the remaining shards, as well 
as computing the expected level of error between the distance from the $k$-th closest neighbor in the first shard and the 
actual $k$-th closest neighbor, are topics for future work.

>>>>

\subsection {Sharding and Auto-Tuning}
\label{subsec:methods:index-building}
In this work, we also introduce the method of \emph{sharding} for datasets that cannot 
fit in memory. With this approach, we begin by

% In this work, we also introduce the method of \emph{sharding} for $k$-nearest neighbors search.
% With this approach, we aim to leverage the fact that $\rho$-nearest neighbors search is typically 
% much faster than $k$-nearest neighbors search.

% We begin by randomly partitioning the dataset into $s$ shards, where $s$ is determined based 
% on some naive auto-tuning. On the first shard, we perform 
% $k$-nearest neighbors search using one of the four algorithms described in Section~\ref{subsec:methods:knn-search}.
% The result of this search will give us the $k$ closest neighbors to the query \emph{in the first shard}. We take the furthest of 
% those $k$ neighbors and use its distance from the query as the radius to be used with $\rho$-nearest neighbors search (see Section~\ref{subsec:methods:rnn-search}) 
% on each remaining shard. We then take the union of the results of these $\rho$-nearest neighbors searches, along with the $k$ neighbors
% from the first shard, and then linear search over those points to find the actual $k$ nearest neighbors.

% Note that the size of the shards is not necessarily consistent; it is often optimal to have the first shard be smaller than the others,
% since the first shard is the only one for which we perform $k$-nearest neighbors search. However, making this first shard too small
% introduces the risk of significantly overestimating the radius (i.e., the distance to the $k$-th ), resulting in much slower $\rho$-nearest neighbors search on the subsequent shards.
% Finding the precise optimal ratio between the size of the first shard and the size of the remaining shards, as well 
% as computing the expected level of error between the distance from the $k$-th closest neighbor in the first shard and the 
% actual $k$-th closest neighbor, are topics for future work.
